Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2017-10-27 paper/main.tex
Fixing stuff

We ran all experiments on a NVIDIA K80 GPU, with five runs per configuration
allowing us to find the average and standard deviation of the time and number of
iterations to convergence. We continually generated random sequences to serve
as input data.  A brief search over learning rate
and batch size was carried out to find the parameters which allow the network to
converge most rapidly for all runs. The criterion for convergence was five consecutive
minibatches giving 100\% accuracy. The learning curves
in figure \ref{fig:synthetic_training} give support to this being a reasonable
convergence criteria.
For the longest sequence length, we did not observe the CuDDN converging, even after
several days' training.
\begin{table}[]
\centering
\caption{Performance of the GILR-LSTM compared to the CuDNN-LSTM
  on problem 2b from \citet{hochreiter1997long}. We see that the GILR-LSTM has a
  clear advantage in training speed as the sequence length increases.  We did
  not observe the Cudnn-LSTM converging for the longest task, even after several
  days.}
\label{table:synth-table}
\begin{tabular}{@{}lllllll@{}} \toprule Sequence Length &
\multicolumn{2}{c}{\textbf{1,024}} & \multicolumn{2}{c}{\textbf{8,192}} &
\multicolumn{2}{c}{\textbf{1,048,576}} \\ \midrule &CuDNN& GILR &
CuDNN &GILR&CuDNN&GILR\\ \cmidrule(l){2-7} Iterations (1000s) &
                     1.0 %bs=8
                     \(\pm\) 0.4 & 0.55 %bs=8
                                    \(\pm\) 0.04 & 0.44 %bs=8
                                                   \(\pm\) 0.05 & 0.56 %bs=8
                                                                 \(\pm\) 0.16
                                                               &-& 14 \(\pm\) 3 \\
\begin{tabular}[c]{@{}l@{}}Wall time (hours)\end{tabular} &
0.28 \(\pm\) 0.08 & 0.031 \(\pm\) 0.002 & 0.58 \(\pm\) 0.06 & 0.10 \(\pm\) 0.03
&-& 9.7 \(\pm\) 1.7 \\ \bottomrule
\end{tabular}
\end{table}

>>>>

We ran all experiments on a NVIDIA K80 GPU, with five runs per configuration
allowing us to find the average and standard deviation of the time and number of
iterations to convergence. We continually generated random sequences to serve
as input data.  A brief search over learning rate
and batch size was carried out to find the parameters which allow the network to
converge most rapidly for all runs. The criterion for convergence was five consecutive
minibatches giving 100\% accuracy. The learning curves
in figure \ref{fig:synthetic_training} give support to this being a reasonable
convergence criteria.
For the longest sequence length, we did not observe the CuDNN LSTM converging, even after
several days' training.

\begin{table}[]
\centering
\caption{Performance of the GILR-LSTM compared to the CuDNN LSTM
  on problem 2b from \citet{hochreiter1997long}. }
\label{table:synth-table}
\begin{tabular}{@{}lllllll@{}} \toprule Sequence Length &
\multicolumn{2}{c}{\textbf{1,024}} & \multicolumn{2}{c}{\textbf{8,192}} &
\multicolumn{2}{c}{\textbf{1,048,576}} \\ \midrule &CuDNN& GILR &
CuDNN &GILR&CuDNN&GILR\\ \cmidrule(l){2-7} Iterations (1000s) &
                     1.0 %bs=8
                     \(\pm\) 0.4 & 0.55 %bs=8
                                    \(\pm\) 0.04 & 0.44 %bs=8
                                                   \(\pm\) 0.05 & 0.56 %bs=8
                                                                 \(\pm\) 0.16
                                                               &-& 14 \(\pm\) 3 \\
\begin{tabular}[c]{@{}l@{}}Wall time (hours)\end{tabular} &
0.28 \(\pm\) 0.08 & 0.031 \(\pm\) 0.002 & 0.58 \(\pm\) 0.06 & 0.10 \(\pm\) 0.03
&-& 9.7 \(\pm\) 1.7 \\ \bottomrule
\end{tabular}
\end{table}
